---
title: "Supplement 2"
subtitle: "Baseline characteristics of RCTs for neuropathic pain"
author: "Peter Kamerman"
date: "Last knitted: `r format(Sys.Date(), '%d %B %Y')`"
---

```{r set_up, include = FALSE}
# Load packages
library(tidyverse)
library(spatstat.geom)
library(boot)
library(skimr)

# Output options
if(!dir.exists('figures')){
  dir.create('figures')  
} 

if(!dir.exists('figures/supplement-1-baseline-calculations/')){
  dir.create('figures/supplement-1-baseline-calculations/')  
} 

# Set options
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.height = 5,
                      fig.width = 7, 
                      fig.path = 'figures/supplement-1-baseline-calculations/')
```

----

# Pain intensity inclusion thresholds

- Original data source: Finnerup et al 2015, Appendix 4[^1].

    - All numeric values were used (after removing duplicate entries).

    - All visual analogue values were converted to a 0 to 10 scale.

[^1]: Finnerup NB, Attal N, Haroutounian S, McNicol E, Baron R, Dworkin RH, Gilron I, Haanpää M, Hansson P, Jensen TS, Kamerman PR, Lund K, Moore A, Raja SN, Rice ASC, Rowbotham M, Sena E, Siddall P, Smith BH, Wallace M. Pharmacotherapy for neuropathic pain in adults: a systematic review and meta-analysis. Lancet Neurol 2015;14:162–173. doi:10.1016/S1474-4422(14)70251-0

```{r thresholds}
# Inclusion criteria thresholds extracted from the supplementary 
# materials of Finnerup et al., 2015
cut_off <- c(5, 4, 4, 2, 4, 3, 4, 6, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 
             4, 6, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 
             4, 4, 4, 4, 4, 4, 4, 3, 3, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 5, 3, 4, 
             4, 4, 4, 4, 4, 4, 4, 4, 5, 5, 5, 5, 4, 4, 4, 3, 5, 4, 4, 4, 5, 5,
             4, 4, 5, 3, 4, 4, 4, 5, 4, 3, 3, 3, 3, 3, 3, 3, 4, 7, 5, 4, 3, 2,
             3, 4, 4, 2.5, 2.5, 4, 4, 4, 4, 5, 4, 4, 8, 4, 4, 4, 5, 3, 4, 4, 4)

# Generate summary statistics
## 6-number summary
summary(cut_off)

## Tabular summary of inclusion thresholds
data.frame(cutoff = cut_off) %>% 
    group_by(cutoff) %>% 
    summarise(count = n(),
              percent = round(100 * (count/length(cut_off)), 1)) %>% 
    knitr::kable(., caption = 'Summary of pain inclusion thresholds')
```

----

# Explore baseline pain intensity data

## Import data

- Original data source: Finnerup et al 2015, Appendix 4$^1$,

```{r import data}
data <- read_csv('data/baseline-data.csv')
```

## Explore data 

### Median

```{r median_explore}
data %>% 
    filter(mean_or_median == 'median') %>% 
    summarise(min = round(min(value, na.rm = TRUE), 1),
              Q25 = round(quantile(value, probs = 0.25, na.rm = TRUE), 1),
              mean = round(mean(value, na.rm = TRUE), 1),
              median = round(median(value, na.rm = TRUE), 1),
              Q75 = round(quantile(value, probs = 0.75, na.rm = TRUE), 1),
              max = round(max(value, na.rm = TRUE), 1)) %>% 
    knitr::kable(., caption = 'Summary: median values')
```

### Mean

```{r mean_explore}
data %>% 
    filter(mean_or_median == 'mean') %>% 
    summarise(min = round(min(value, na.rm = TRUE), 1),
              Q25 = round(quantile(value, probs = 0.25, na.rm = TRUE), 1),
              mean = round(mean(value, na.rm = TRUE), 1),
              median = round(median(value, na.rm = TRUE), 1),
              Q75 = round(quantile(value, probs = 0.75, na.rm = TRUE), 1),
              max = round(max(value, na.rm = TRUE), 1)) %>% 
    knitr::kable(., caption = 'Summary: mean values')
```

### SD

```{r sd_explore}
data %>% 
    filter(!is.na(sd)) %>% 
    summarise(min = round(min(sd, na.rm = TRUE), 1),
              Q25 = round(quantile(sd, probs = 0.25, na.rm = TRUE), 1),
              mean = round(mean(sd, na.rm = TRUE), 1),
              median = round(median(sd, na.rm = TRUE), 1),
              Q75 = round(quantile(sd, probs = 0.75, na.rm = TRUE), 1),
              max = round(max(sd, na.rm = TRUE), 1)) %>% 
    knitr::kable(., caption = 'Range of SD values')
```

----

# Weighted medians 

- Three studies, four median values.

- Hahn et al., 2004 (active), Hahn et al., 2004 (placebo), Yuen et al., 2002, Low et al., 1995

```{r median}
# Process data
median <- data %>% 
    filter(included_in_analysis == 'yes') %>% 
    filter(mean_or_median == 'median') %>% 
    # Calculate total sample size
    mutate(total_sample = sum(sample_size)) %>% 
    # Calculate weights
    mutate(weights = sample_size / total_sample)
    
## Weighted median
weighted.median(x = median$value, 
                w = median$weights)
```

----

# Pooled mean

- Formula sourced from: https://www.ncbi.nlm.nih.gov/books/NBK56512/

```{r pooled_mean}
# Make bootstrap function
pooled_mean <- function(d, i){
    # Select data
    data <- d[i, ]
    
    # Process data
    mean <- data %>% 
      # Get the required data
      filter(included_in_analysis == 'yes') %>% 
      filter(mean_or_median == 'mean')
    
    # Calculate preliminary values
    mean <- mean %>% 
      mutate(mean_by_n = value * sample_size)
    
    # Calculate pooled mean
    sum(mean$mean_by_n) / sum(mean$sample_size)
}

# Perform bootstrap
set.seed(2019)
mean_pooled <- boot(data = data, 
                    statistic = pooled_mean, 
                    R = 999, 
                    stype = 'i',
                    parallel = 'multicore',
                    ncpus = 4)

# Pooled mean 
mean_pooled$t0

# Confidence interval of the pooled mean (percentile method)
boot.ci(mean_pooled, type = 'perc')
```

----

# Pooled SD

- Formula sourced from: https://www.ncbi.nlm.nih.gov/books/NBK56512/

```{r pooled_sd}
# Make bootstrap function
pooled_sd <- function(d, i){
    # Select data
    data <- d[i, ]
    
    # Process the data 
    sd <- data %>% 
      filter(included_in_analysis == 'yes') %>% 
      filter(mean_or_median == 'mean') %>% 
      filter(!is.na(sd)) %>% 
      # Square the SD
      mutate(SD_squared = sd^2) %>% 
      # Calculate sample size -1
      mutate(n_minus_1 = sample_size - 1) %>% 
      # Get the number of groups
      mutate(k = length(unique(.$authors))) %>% 
      # Calculate (n-1)SD^2
      mutate(numerator = SD_squared * n_minus_1)
  
    # Pooled SD
    sqrt(sum(sd$numerator) / (sum(sd$sample_size) - sd$k[[1]]))
}

# Perform bootstrap
set.seed(2019)
sd_pooled <- boot(data = data, 
                    statistic = pooled_sd, 
                    R = 999, 
                    stype = 'i',
                    parallel = 'multicore',
                    ncpus = 4)

# Pooled mean 
sd_pooled$t0

# Confidence interval of the pooled mean (percentile method)
boot.ci(sd_pooled, type = 'perc')
```

----

# Mean placebo reponse

## DPN/PHN

- Freeman R, Emir B, Parsons B. Predictors of placebo response in peripheral neuropathic pain: insights from pregabalin clinical trials. _J Pain Res_ **8**:257–268, 2015. DOI:10.2147/JPR.S78303.

```{r}
# Taken from Table 2 (all placebo response values are LS means)
freeman_placebo <- c(1.16, 1.35, 1.93, 0.88, 1.77, 1.78, 2.54, 1.62, 
                     2.32, 2.32, 0.97, 0.52, 1.06, 0.53, 1.86,
                     1.60, 1.65)

freeman_size <- c(82, 97, 80, 69, 93, 46, 134, 83, 149, 
                  70, 87, 81, 84, 93, 16, 83, 32)

length(freeman_placebo)

df_placebo <- data.frame(value = freeman_placebo,
                         size = freeman_size) %>%
  mutate(value_size = value * size)

# Weighted mean
sum(df_placebo$value_size) / sum(df_placebo$size)
```

## chronic OA/LBP

- Vase L, Vollert J, Finnerup NB, Miao X, Atkinson G, Marshall S, Nemeth R, Lange B, Liss C, Price DD, Maier C, Jensen TS, Segerdahl M. Predictors of the placebo analgesia response in randomized controlled trials of chronic pain: a meta-analysis of the individual data from nine industrially sponsored trials. _Pain_ **156**:1795–1802, 2015. DOI:10.1097/j.pain.0000000000000217.

```{r}
# Taken from Figure 1 
scale_placebo = 5/42
vase_placebo <- c(89, 146, 62, 97.5, 48, 52.5, 131, 155.5, 141.5) + 42
vase_placebo <- round(scale_placebo * vase_placebo)
vase_placebo <- vase_placebo / 10 # Conversion from 100mm VAS to 10 unit NRS 

scale_size = 50/15
vase_size <- c(35, 37, 37, 65, 65, 72.5, 95, 100, 100)
vase_size <- round(vase_size * scale_size)

length(vase_placebo)

df_placebo2 <- data.frame(value = vase_placebo,
                          size = vase_size) %>%
  mutate(value_size = value * size)

# Weighted mean
sum(df_placebo2$value_size) / sum(df_placebo2$size)
```

----

# Session information

```{r session_info}
sessionInfo()
```